### 2022-07-26 Papers/ICCC-2023/sections/design.tex
stuff

\section{Language and compiler design}
\label{language-compiler-design}

CTFE First apporach was created during implementation of the first compiler for the C-=-1 language\cite{grabski2022compilation}.
The need for a new approach to compiler construction arose due to the unusal characteristics of the language, further described in chapter \ref{language-design}.
Chapter \ref{compiler-design} describes the CTFE First approach and how the compiler is structured.

\subsection{Design of C-=-1}
\label{language-design}

@@

\subsubsection{Type system}

\subsubsection{Attributes and metaprogramming}

\subsection{Design of the compiler}
\label{compiler-design}

CTFE First compiler has four major components: Frontend, Interpreter, Compiler Interface and Backend.
Figure \ref{CTFE-first-compiler-structure} contains a diagram with an overview of how these pieces interact with eachother, during the compilaton process.
Frontend, described in chapter \ref{frontend}, parses the code in the compiled language and constructs its intermidaite representation, using interpreter's data structures.
It is used to analyze both user code and the Compiler Interface.
After the intermidiate representation is constructed, it is passed on to the Interpreter, which was described in chapter \ref{interpreter}.
Compiler Interface intermidiate representation is then executed, using the user program as data. 
This step converts the semantic model of the program into the backends intermidiate language.
This process has been further explained in chapter \ref{compiler-interface}.
Finaly the Backend generates the executable file.

@@

\subsubsection{Frontend}
\label{frontend}

In the CTFE First approach, frontend serves the same role of constructing the programs intermidiate representation, as in conventional compilers \cite{puntambekar:compiler_design}.

\subsubsection{Interpreter}
\label{interpreter}

\subsubsection{Compiler interface} 
\label{compiler-interface}

\subsubsection{Backend}
\label{backend}

>>>>

\section{Design of C-=-1}
\label{language-design}

@@

\subsection{Type system}

\subsection{Attributes and metaprogramming}

\section{Design of the compiler}
\label{compiler-design}

CTFE First apporach was created during implementation of the first compiler for the C-=-1 language\cite{grabski2022compilation}.
CTFE First compiler has four major components: Frontend, Interpreter, Compiler Interface and Backend.
Figure \ref{CTFE-first-compiler-structure} contains a diagram with an overview of how these pieces interact with eachother, during the compilaton process.
Frontend, described in chapter \ref{frontend}, parses the code in the compiled language and constructs its intermidaite representation, using interpreter's data structures.
It is used to analyze both user code and the Compiler Interface.
After the intermidiate representation is constructed, it is passed on to the Interpreter, which was described in chapter \ref{interpreter}.
Compiler Interface intermidiate representation is then executed, using the user program as data. 
This step converts the semantic model of the program into the backends intermidiate language.
This process has been further explained in chapter \ref{compiler-interface}.
Finaly the Backend generates the executable file.

@@

\subsection{Frontend}
\label{frontend}

In the CTFE First approach, frontend serves the same role of constructing the programs intermidiate representation, as in conventional compilers \cite{puntambekar:compiler_design}.
The major difference lays in the data structures used to represent the program.

\subsection{Interpreter}
\label{interpreter}

\subsection{Compiler interface} 
\label{compiler-interface}

\subsection{Backend}
\label{backend}

### 2022-07-26 Papers/ICCC-2023/sections/implementation.tex
some more stuff
design
stuff

\section{Implementation}

@@

@@

\subsection{Backend interface}

>>>>

\section{Implementation}
\label{implementation}

The first CTFE First was created for the C-=-1 language, using out-of-the-box parser generator and backend.

@@

Data structures of the C-=-1 Interpreter have been designed ease of development and debugging in mind.
They are thus not particularly efficent.

\begin{figure}
	\includegraphics[width=8cm]{pictures/interpreter_data_structures_uml.png}
	\caption{Class diagram of C-=-1 interpreter data structures}
	\label{fig:interpreter_data_structures}
\end{figure}

Figure \ref{fig:interpreter_data_structures} contains a class diagram of most of the types used to represent values within C-=-1.

@@

\subsection{Backend interface}
\label{implementation/backend-interface}

### 2022-07-26 Papers/ICCC-2023/sections/introduction.tex
stuff

CTFE first builds the compiler around the interpreter component.
The role of the compiler is to construct the semantic model of the program being compiled and pass it as data to the interpreted Compiler-Intreface module.
Compiler-Interface then tranforms the model into the backend's assembly language to be compiled to executable.
Structure of the compiler and its influence on the language design is further discussed in chapter \ref{language-compiler-design}.

>>>>

CTFE first builds the compiler around the interpreter component.
The role of the compiler is to construct the semantic model of the program being compiled and pass it as data to the interpreted Compiler-Intreface module.
Compiler-Interface then tranforms the model into the backend's assembly language to be compiled to executable.
The design of the language that sparked this approach was described in chapter \ref{language-design}.
Chapter \ref{compiler-design} deals with structure of a CTFE First compiler and how its components interact.
